The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-04-01 doc/paper/paper2d.tex
example of superflat

where $A$ is a overall normalization in counts, 
$SF$ is the average wavelength dependent response called the ``superflat'', and
${\rm fiber~flat_i}$ is the fiber-to-fiber response as a function of wavelength.
This model of the extracted flat-field spectra provides a transformation to
compare detected counts from one fiber to another.

This should remove the differential response due to the individual fiber
throughput, as well as the small relative differences in the size of the
spectral pixels at a constant wavelength.  ??Why do we correct for pixel
sizes later on if the differential wavelength dispersion is included in fflat??

The common normalized response, $f_{avg}$, is specified as a B-spline
function with breakpoints spaced approximately every native pixels.
An example of normalized individual fiber spectra 
and the resulting B-spline fit are shown in Figure ?.  The individual fiber
flat vectors are fits to the ratio of the extracted spectra to the superflat
(define above).  The individual vector fits are also B-splines with breakpoints
spaced approximately every 5 native pixels.  The final set of flat vectors are
stored as an image with dimensions Nfiber x Npixels.

@@

>>>>

where $A$ is a overall normalization in counts, 
$SF$ is the average wavelength dependent response called the ``superflat'', and
${\rm fiber~flat_i}$ is the fiber-to-fiber response as a function of wavelength.
This model of the extracted flat-field spectra provides a transformation to
compare detected counts from one fiber to another.
The flat-field vectors correct the differential response due to the individual fiber
throughput, as well as the small relative differences in the size of the
spectral pixels at a constant wavelength.

The common normalized response, $SF$, is specified as a B-spline
function with breakpoints spaced approximately every native pixels.
An example of normalized individual fiber spectra 
and the resulting B-spline fit are shown in Figure 2.  The individual fiber
flat vectors are fits to the ratio of the extracted spectra to the superflat
(define above).  The individual vector fits are also B-splines with breakpoints
spaced approximately every 5 native pixels.  The final set of flat vectors are
stored as an image with dimensions Nfiber x Npixels.

@@

\begin{figure}[tb]
\figurenum{1}
\epsscale{1.0}
\plotone{plate_stats.ps}
\figcaption{Observational summary of the 1656 publicly released
SDSS spectroscopic
plates observed between MJD 2451600 to 2453600.  Each plate is
represented by 3 symbols showing the median RMS guiding residuals
in the 11 guide fibers in arcseconds (diamonds), 
the median seeing of the 11 guide star PSFs in arcseconds (stars), 
and the effective (S/N)$^2$ of the plate observation
normalized to a 1 hour exposure.  Vertical lines show the date of July 15 across
the years of 2000 to 2005.
\label{fig1}
}
\end{figure}

\begin{figure}[tb]
\figurenum{2}
\epsscale{1.0}
\plotone{spDiag2d-0412-52258.ps_1}
\figcaption{A typical example of the common flat-field spectra, $SF$,
for the b1 camera observations of plate 412.  The solid line is the best-fit
B-spline function, and the red points are rejected 2-sigma outliers. 
\label{fig2}
}
\end{figure}
